---
title: "Report"
author: "Silvia Ferrer and Ignacio Lloret"
date: "2023-11-27"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)
library(DataExplorer)
library(dplyr)
library(mice)
library(chemometrics)
library(car)

# Clear plots
if(!is.null(dev.list())) dev.off()

# Clean workspace
rm(list=ls())

df1 <- read.csv("../data/data2.txt")
#df1 <- read.csv("../data/data.xls")


df1 %>% glimpse

```

# Data Preparation
## Missing data and Errors
Checking the missing data in the dataset and which variables have NA’s we can see that the ones with missing values is TotalCharges.
Vemos que los missings del TotalCharges son debido a que los meses que el cliente ha estado en la compañia (tenure) son 0. Entonces, totalCharges será 0 hasta que empiece el contrato, es decir que empiece el primer mes de contrato y tenure sea 1.
```{r, missing_data}
#, fig.height=1.5

# Duplicates observations
df1 <- distinct(df1, .keep_all = TRUE)

# Numeric to factor SeniorCitizen
df1$SeniorCitizen <- df1$SeniorCitizen %>% as.factor()

# Take off the variable customerID
df1 <- subset(df1, select = -customerID)

cat_keep <- names(df1)[sapply(df1, function(x) is.character(x))]
numeric_columns <-  names(df1)[sapply(df1, function(x) is.numeric(x))]

df1[cat_keep] <- lapply(df1[cat_keep], as.factor) ## Create Factors
df1[numeric_columns] <- lapply(df1[numeric_columns], as.numeric)

# Missing values
plot_missing(df1, missing_only = TRUE, group = list("Low" = 0.05, "Medium"=0.25, "High"=0.5, "Very High" =1), geom_label_args = list("size" = 2))

observaciones_na <- df1 %>% filter(is.na(TotalCharges))
print(observaciones_na$tenure)

# Errors or inconsistencies
df1$TotalCharges <- ifelse(is.na(df1$TotalCharges) & df1$tenure == 0, 0, df1$TotalCharges)

#inconsistencias con el No phone service o No internet service
summary(df1) # misma frec de no phone y internet service en las variables
```

# Variable analysis
## Categorical values
```{r, categorical_plot}
p1 <- df1 %>% 
  select(all_of(cat_keep)) %>%
  pivot_longer(cols=everything()) %>%
  ggplot(data=.) +
  geom_bar(aes(x=value), col="black", fill="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~name, scales="free", ncol=4)
p1

```

## Numerical Data

```{r, num_graphs}
#, fig.height=20
p2 <- df1 %>% 
  select(all_of(numeric_columns)) %>%
  pivot_longer(cols=everything()) %>%
  ggplot(data=.) +
  geom_boxplot(aes(y=value), col="black", fill="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~name, scales="free", ncol=4)
p2

# Create a discretization of numeric variables
sm <- summary(df1$tenure)
df1$f.tenure <- ifelse(df1$tenure <= sm["1st Qu."], 1, 
               ifelse(df1$tenure > sm["1st Qu."] & df1$tenure <= sm["Mean"], 2,
               ifelse(df1$tenure > sm["Mean"] & df1$tenure <= sm["3rd Qu."], 3, 
               ifelse(df1$tenure > sm["3rd Qu."], 4,0))))
df1$f.tenure <- factor(df1$f.tenure, labels=c("LowTenure","LowMidTenure","HighMidTenure","HighTenure"), order = T, levels=c(1,2,3,4))
table(df1$f.tenure)

sm <- summary(df1$MonthlyCharges)
df1$f.MonthlyCharges <- ifelse(df1$MonthlyCharges <= sm["1st Qu."], 1, 
               ifelse(df1$MonthlyCharges > sm["1st Qu."] & df1$MonthlyCharges <= sm["Mean"], 2,
               ifelse(df1$MonthlyCharges > sm["Mean"] & df1$MonthlyCharges <= sm["3rd Qu."], 3, 
               ifelse(df1$MonthlyCharges > sm["3rd Qu."], 4,0))))
df1$f.MonthlyCharges <- factor(df1$f.MonthlyCharges, labels=c("LowMonthlyCharges","LowMidMonthlyCharges","HighMidMonthlyCharges","HighMonthlyCharges"), order = T, levels=c(1,2,3,4))
table(df1$f.MonthlyCharges)

sm <- summary(df1$TotalCharges)
df1$f.TotalCharges <- ifelse(df1$TotalCharges <= sm["1st Qu."], 1, 
               ifelse(df1$TotalCharges > sm["1st Qu."] & df1$TotalCharges <= sm["Mean"], 2,
               ifelse(df1$TotalCharges > sm["Mean"] & df1$TotalCharges <= sm["3rd Qu."], 3, 
               ifelse(df1$TotalCharges > sm["3rd Qu."], 4,0))))
df1$f.TotalCharges <- factor(df1$f.TotalCharges, labels=c("LowTotalCharges","LowMidTotalCharges","HighMidTotalCharges","HighTotalCharges"), order = T, levels=c(1,2,3,4))
table(df1$f.TotalCharges)
```
# Data Quality Report

## Imputation Missing data
HE CAMBIADO LOS NA'S DE TOTALCHARGES ASI QUE ESTE APARTADO CAMBIA
We decided to impute it with mice and to validate it with summary and plot. We observe that the imputation doesn’t have a significant change in the density nor the summary.
```{r}
#summary(df1)
sum(is.na(df1$TotalCharges))

#imputation - mice
mice_imp<-mice(df1,method = "cart")
df2<-complete(mice_imp)

#validation
summary(df2$TotalCharges)
summary(df1$TotalCharges)
par(mfrow=c(1,2))
plot(density(df1$TotalCharges,na.rm=TRUE), main = "Density TotalCharges", 
     xlab = "TotalCharges", ylab = "Density")
plot(density(df2$TotalCharges,na.rm=TRUE), main = "Density Imputed TotalCharges", 
     xlab = "TotalCharges", ylab = "Density")
```

## Univariate outliers variable
crear variable de recuento de outliers para mirar correlations



## Multivariate outliers
A threshold of 0.5% is chosen as signficance level because this returns some outliers.
Como se muestra en la comparacion de summary, los multivariate outliers son personas que no son senior citizen, tienen pareja y personas dependientes mayoritariamente, todas tienes phone service, ninguno tiene internet service, tienen un contrato de 2 años y ninguno ha churned.
```{r}
df2 <- df1
df_of_interest <- df2[,c(numeric_columns)]

res.out = Moutlier(df_of_interest, quantile = 0.995, col="green") #0.9995

which((res.out$md > res.out$cutoff)&(res.out$rd > res.out$cutoff))
length(which((res.out$md > res.out$cutoff)&(res.out$rd > res.out$cutoff)))

par(mfrow=c(1,1))
plot( res.out$md, res.out$rd )
abline(h=res.out$cutoff, col="red")
abline(v=res.out$cutoff, col="red")

summary(df2[which((res.out$md > res.out$cutoff)&(res.out$rd > res.out$cutoff)),])
summary(df2)

# Que hacemos con los multivariate? nos esperamos a la influential plot? Son 9 outliers
#df2 = df2[-which((res.out$md > res.out$cutoff)&(res.out$rd > res.out$cutoff)),]
```

## Model Fitting
To create a model, first we split the train data (df2) into train_new and test_new. We need the test_new to validate the accuracy of the model with data that has the target variable and the model has not used, to check if the model has overfitting

```{r}
set.seed(123)
rows <- sample(nrow(df2), .7 * nrow(df2))
train_new <- df2[rows, ]
test_new <- df2[-rows, ]

```

